Comprehensive Quality Awareness Automated Semantic Web Service Composition

### 2017-03-17 paper.tex
update

\documentclass{IEEEtran}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{color,graphicx,epstopdf,changepage,amsmath,multirow}
\usepackage[justification=centering]{caption}
\SetAlgoCaptionSeparator{.\space}
\renewcommand\AlCapFnt{\normalfont\scshape}
\setlength{\algomargin}{0.7cm}

\title{Comprehensive Quality-Aware Automated Semantic Web Service Composition}
\author{Chen Wang, Hui Ma, Aaron Chen\\ \small School of
Engineering and Computer Science, Victoria University of Wellington, New Zealand\\
Email: \{chen.wang, hui.ma, aaron.chen\}@ecs.vuw.ac.nz}

@@

Existing works on service composition focus mainly on addressing one of challenges above. Many works have been conducted to optimise the quality of compositions under a pre-defined abstract workflow, which is generally considered as a \textit{semi-automated Web service composition} approach \cite{parejo2008qos,bahadori2009optimal}. Meanwhile, many research works consider the possibility of generating a composition plan automatically in discovering and selecting suitable web services, which are considered to be NP-hard \cite{moghaddam2014service}. \textit{Semantic web services composition} is distinguished from the syntactic service composition, which supplements well defined semantic descriptions from the concept of ontologies, instead of parameters value. In the past few years, substantial works have been done on semantic web service composition \cite{boustil2014semantic, mier2015integrated, bansal2016generalized}. However, few works have enabled truely automatic semantic web service composition, where both QoS and quality of semantic match making will be optimised simultaneously and achieved a desired balance.

@@

\section{Related Work} \label{relatedWork}
Substantial work on web service composition focused on either semantic web service composition \cite{boustil2014semantic,mier2015integrated, bansal2016generalized} or QoS-aware web service composition \cite{da2016particle,da2015graphevol,yu2013adaptive, gupta2015optimization,qi2010combining,ma2015hybrid}, However few researchers addressed both semantic matchmaking quality and QoS requirements at the same time for web service composition problems. To the best of our knowledge, \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune} reported some recent attempts on service composition that considers both aspects.

\cite{boustil2014semantic,mier2015integrated, bansal2016generalized} captures the semantics of web services' parameters using some kind of logic (e.g., description logic) for enabling semantic web service composition, where the number of web services or length of the graph is minimised to reach the optimised graph-based composition solutions. However, these approaches need to be improved for the scalability that considering a large number of web services, and the evaluation method does not fit properly for customers' complex requirements.

@@

In summary, composition solutions from semantic web service composition \cite{boustil2014semantic,mier2015integrated, bansal2016generalized} does not consider QoS, and QoS-aware web service composition \cite{da2016particle,da2015graphevol,yu2013adaptive, gupta2015optimization,qi2010combining,ma2015hybrid} does not consider distinguished matchmaking quality in their fitness function. Few works do consider both quality aspects, but some limitations lie in semi-automated approach \cite{lecue2009optimizing}, less general semantic quality measurement \cite{lecue2009optimizing, pop2009immune}, or semantic matchmaking types ignorance \cite{pop2009immune}. In addition, experiments design for  \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune} are not conducted using benchmark dataset for the scalability, only small datasets are utilised that might suffer scalability. Results analysis for \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune} also do not evidently point out what desired balance could be reached by considering semantic matchmaking quality and QoS. Therefore, we proposed a general comprehensive quality model which achieve a more desirable balance in consideration of both semantic matchmaking quality and QoS to fill the gaps discussed above, and then we proposed a POS-based method with explicit support for the comprehensive model, and evaluate its performance by comparing with one existing GP-based approach.

@@

\section{Results and Analysis}\label{results_analysis}
\subsection{Comparison Test with QoS Evaluation Model}\label{comparisonTest}
QoS-aware web service composition \cite{da2016particle,da2015graphevol,yu2013adaptive,ma2015hybrid} do consider two semantic matchmaking types (Exact and Plugin) for discovering desired web service, but there is no measurement of matchmaking types and concept similarity, so the weights for $MT$ and $S$ are considered to be 0. Consequently, our evaluation mode become a widely used fitness function \cite{ma2015hybrid, da2016particle}, $Fitness = w_1 \hat{A} + w_2 \hat{R} + w_3(1 - \hat{T}) + w_4(1 - \hat{C})$ when $\sum_{i=1}^{4} w_i = 1$  for QoS-aware web service composition. To compare the composition solution generated by our approach with QoS-aware approach. We look at mean value of $MT$, $S$ and $QoS$ at optimum at the 100th generation for two approaches. In QoS-aware approach, $MT$ and $S$ are recorded, and $QoS$ is normalised from 0 to 0.5 to make it comparable, besides that, all weights in QoS-aware fitness function are set equally to 0.25.

@@

\bibliographystyle{IEEEtran}
\bibliography{IEEEexample}

>>>>

\documentclass{llncs}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{color,graphicx,epstopdf,changepage,amsmath,multirow}
\usepackage[justification=centering]{caption}
\SetAlgoCaptionSeparator{.\space}
\renewcommand\AlCapFnt{\normalfont\scshape}
\setlength{\algomargin}{0.7cm}

\title{Comprehensive Quality Awareness Automated Semantic Web Service Composition}
\author{Chen Wang, Hui Ma, and Aaron Chen}
\institute{School of Engineering and Computer Science,
\\Victoria University of Wellington, New Zealand \\
Email: \{chen.wang, hui.ma, aaron.chen\}@ecs.vuw.ac.nz}

@@

Existing works on service composition focus mainly on addressing one of challenges above. Many works have been conducted to optimise the quality of compositions under a pre-defined abstract workflow, which is generally considered as a \textit{semi-automated Web service composition} approach \cite{bahadori2009optimal,parejo2008qos}. Meanwhile, many research works consider the possibility of generating a composition plan automatically in discovering and selecting suitable web services, which are considered to be NP-hard \cite{moghaddam2014service}. \textit{Semantic web services composition} is distinguished from the syntactic service composition, which supplements well defined semantic descriptions from the concept of ontologies, instead of parameters value. In the past few years, substantial works have been done on semantic web service composition \cite{bansal2016generalized,boustil2014semantic,mier2015integrated}. However, few works have enabled truely automatic semantic web service composition, where both QoS and quality of semantic match making will be optimised simultaneously and achieved a desired balance.

@@

\section{Related Work} \label{relatedWork}
Substantial work on web service composition focused on either semantic web service composition \cite{boustil2014semantic,mier2015integrated,bansal2016generalized} or QoS-aware web service composition \cite{da2016particle,da2015graphevol,yu2013adaptive,gupta2015optimization,qi2010combining,ma2015hybrid}, However few researchers addressed both semantic matchmaking quality and QoS requirements at the same time for web service composition problems. To the best of our knowledge, \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune} reported some recent attempts on service composition that considers both aspects.

\cite{boustil2014semantic,mier2015integrated,bansal2016generalized} captures the semantics of web services' parameters using some kind of logic (e.g., description logic) for enabling semantic web service composition, where the number of web services or length of the graph is minimised to reach the optimised graph-based composition solutions. However, these approaches need to be improved for the scalability that considering a large number of web services, and the evaluation method does not fit properly for customers' complex requirements.

@@

In summary, composition solutions from semantic web service composition \cite{bansal2016generalized,boustil2014semantic,mier2015integrated} does not consider QoS, and QoS-aware web service composition
\cite{gupta2015optimization,ma2015hybrid,da2016particle,da2015graphevol,yu2013adaptive} does not consider distinguished matchmaking quality in their fitness function. Few works do consider both quality aspects, but some limitations lie in semi-automated approach \cite{lecue2009optimizing}, less general semantic quality measurement \cite{lecue2009optimizing,pop2009immune}, or semantic matchmaking types ignorance \cite{pop2009immune}. In addition, experiments design for  \cite{fanjiang2014semantic,lecue2009optimizing,pop2009immune} are not conducted using benchmark dataset for the scalability, only small datasets are utilised that might suffer scalability. Results analysis for \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune} also do not evidently point out what desired balance could be reached by considering semantic matchmaking quality and QoS. Therefore, we proposed a general comprehensive quality model which achieve a more desirable balance in consideration of both semantic matchmaking quality and QoS to fill the gaps discussed above, and then we proposed a POS-based method with explicit support for the comprehensive model, and evaluate its performance by comparing with one existing GP-based approach.

@@

\section{Results and Analysis}\label{results_analysis}
\subsection{Comparison Test with QoS Evaluation Model}\label{comparisonTest}
QoS-aware web service composition \cite{da2016particle,da2015graphevol,yu2013adaptive,ma2015hybrid} do consider two semantic matchmaking types (Exact and Plugin) for discovering desired web service, but there is no measurement of matchmaking types and concept similarity, so the weights for $MT$ and $S$ are considered to be 0. Consequently, our evaluation mode become a widely used fitness function \cite{ma2015hybrid,da2016particle}, $Fitness = w_1 \hat{A} + w_2 \hat{R} + w_3(1 - \hat{T}) + w_4(1 - \hat{C})$ when $\sum_{i=1}^{4} w_i = 1$  for QoS-aware web service composition. To compare the composition solution generated by our approach with QoS-aware approach. We look at mean value of $MT$, $S$ and $QoS$ at optimum at the 100th generation for two approaches. In QoS-aware approach, $MT$ and $S$ are recorded, and $QoS$ is normalised from 0 to 0.5 to make it comparable, besides that, all weights in QoS-aware fitness function are set equally to 0.25.

@@

\bibliographystyle{splncs03}
\bibliography{IEEEexample}
